## Calculate the mean values for BMI and blood glucose levels

Using base DataSHIELD we can do:
```{r}
ds.mean("data$LAB_GLUC_ADJUSTED")
ds.mean("data$PM_BMI_CONTINUOUS")
```

Or using dsHelper:
```{r}
stats <- dh.getStats(
  df = "data",
  vars = c("LAB_GLUC_ADJUSTED", "PM_BMI_CONTINUOUS")
)

stats
````
## Make a scatter plot for the same two variables
```{r}
ds.scatterPlot(x = "data$LAB_GLUC_ADJUSTED", y = "data$PM_BMI_CONTINUOUS")
```
## Run a two-stage meta-analysis to see if these variables are associated
```{r}
two_stage_out <- ds.glmSLMA(
  formula = "data$PM_BMI_CONTINUOUS ~ data$LAB_GLUC_ADJUSTED",
  family = "gaussian",
  newobj = "workshop.obj")
```
```{r}
meta_out <- ds.glmSLMA(
  formula = "data$PM_BMI_CONTINUOUS ~ data$LAB_GLUC_ADJUSTED",
  family = "gaussian",
  newobj = "practical")
```

What are the coefficients for `LAB_GLUC_ADJUSTED` for each cohort?
```{r}
two_stage_out$betamatrix.valid
```

## Plot the findings from your meta-analysis in a forest plot.
```{r}
ds.forestplot(
  mod = two_stage_out,
  variable = "data$LAB_GLUC_ADJUSTED"
)
```

## Bonus 1: Make a scatter plot showing the residuals of your model

```{r}
ds.glmPredict(glmname = "practical", newobj = "practical.prediction")
ds.cbind(c('data$PM_BMI_CONTINUOUS', 'data$LAB_GLUC_ADJUSTED'), newobj='practical_vars')
ds.completeCases('practical_vars', newobj='practical_vars.complete')

glmslma <- ds.glmSLMA(
  formula = "practical_vars.complete$PM_BMI_CONTINUOUS ~ practical_vars.complete$LAB_GLUC_ADJUSTED",
  family = "gaussian",
  newobj = "practical.obj")

ds.make(
  toAssign = paste0(
    "(", glmslma$SLMA.pooled.ests.matrix[1,1],")+(",
    glmslma$SLMA.pooled.ests.matrix[2,1], "*practical_vars.complete$LAB_GLUC_ADJUSTED)"),
  newobj = "practical_predicted")

ds.make(
  toAssign = "practical_vars.complete$PM_BMI_CONTINUOUS - practical_predicted",
  newobj = "residuals")

ds.scatterPlot('practical_predicted', "residuals")
```
## Bonus 2: Make a forest plot using a different theme
```{r}
?ds.forestplot
?meta::metagen
?meta::meta

ds.forestplot(
  mod = two_stage_out,
  variable = "data$LAB_GLUC_ADJUSTED",
  layout = "RevMan5")
```
